### 2020-02-26 RFCs/HDF5/VOL/connector_author_guide/connector_interface.tex
Updaed the VOL docs to reflect pending H5Dget_offset() changes.
Former-commit-id: 009dfbff6fdd6976182c1f57ebadfbbe7c7e57e6

The \texttt{get\_type} argument is an \texttt{enum}:
\begin{lstlisting}
/* types for dataset GET callback */
typedef enum H5VL_dataset_get_t {                                                
    H5VL_DATASET_GET_DAPL,                  /* access property list                */
    H5VL_DATASET_GET_DCPL,                  /* creation property list              */
    H5VL_DATASET_GET_OFFSET,                /* offset                              */
    H5VL_DATASET_GET_SPACE,                 /* dataspace                           */
    H5VL_DATASET_GET_SPACE_STATUS,          /* space  status                       */
    H5VL_DATASET_GET_STORAGE_SIZE,          /* storage size                        */
    H5VL_DATASET_GET_TYPE                   /* datatype                            */
} H5VL_dataset_get_t; 
\end{lstlisting}

Note that \texttt{H5VL\_DATASET\_GET\_OFFSET} (used in \texttt{H5Dget\_offset()}) retains
the \texttt{haddr\_t} type and was not updated to use the \texttt{H5O\_token\_t}
type. This enum value and \texttt{H5Dget\_offset()} may be deprecated in a future
version of the HDF5 and replaced with a token-based equivalent.

>>>>

The \texttt{get\_type} argument is an \texttt{enum}:
\begin{lstlisting}
/* types for dataset GET callback */
typedef enum H5VL_dataset_get_t {                                                
    H5VL_DATASET_GET_DAPL,                  /* access property list                */
    H5VL_DATASET_GET_DCPL,                  /* creation property list              */
    H5VL_DATASET_GET_SPACE,                 /* dataspace                           */
    H5VL_DATASET_GET_SPACE_STATUS,          /* space  status                       */
    H5VL_DATASET_GET_STORAGE_SIZE,          /* storage size                        */
    H5VL_DATASET_GET_TYPE                   /* datatype                            */
} H5VL_dataset_get_t; 
\end{lstlisting}
